---
title: "iemiscdata: Viewing Tables & Their Associated Notes"
author: "Irucka Embry, E.I.T. (EcoC²S)"
date: "`r Sys.Date()`"
lang: en-us
urlcolor: blue
output:
  rmarkdown::pdf_document:
    highlight: kate
    toc: true
    latex_engine: xelatex
vignette: >
  %\VignetteIndexEntry{iemiscdata Viewing Tables & Their Associated Notes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

\bigskip

## Load the packages

Note: If you wish to replicate the R code below, then you will need to copy and paste the following commands in R first to make sure you have all the packages loaded:  

```{r, warning = FALSE, message = FALSE, tidy = TRUE}

install.load::load_package("iemiscdata", "pander", "knitr")
# load needed packages using the load_package function from the install.load package (it is assumed that you have already installed these packages)

# set the pander options
panderOptions("missing", "")
panderOptions("table.alignment.default", "left")
panderOptions("table.alignment.rownames", "left")
panderOptions("table.split.cells", Inf)
panderOptions("table.split.table", Inf)

```

\bigskip
\bigskip

# Table 2-1: Runoff depth for selected CN's and rainfall amounts & notes

```{r, warning = FALSE, message = FALSE, tidy = TRUE}

data(runoff_depth)
data(runoff_depth_notes)
# load the data from iemiscdata (containing Table 2-1: Runoff depth for selected CN's and rainfall amounts & notes)

pander(runoff_depth)
pander(runoff_depth_notes)

```

\bigskip
\bigskip

# Table 2-2a: Runoff curve numbers for urban areas & notes

```{r, warning = FALSE, message = FALSE, tidy = TRUE}

data(cn_urban)
data(cn_urban_notes)
# load the data from iemiscdata (containing Table 2-2a: Runoff curve numbers for urban areas & notes)

pander(cn_urban)
pander(cn_urban_notes)

```

\bigskip
\bigskip

# Table 2-2b: Runoff curve numbers for cultivated agricultural lands & notes

```{r, warning = FALSE, message = FALSE, tidy = TRUE}

data(cn_agricultural)
data(cn_agricultural_notes)
# load the data from iemiscdata (containing Table 2-2b: Runoff curve numbers for cultivated agricultural lands & notes)


pander(cn_agricultural)
pander(cn_agricultural_notes)
```

\bigskip
\bigskip

# Table 2-2c: Runoff curve numbers for other agricultural lands & notes

```{r, warning = FALSE, message = FALSE, tidy = TRUE}

data(cn_other_agricultural)
data(cn_other_agricultural_notes)
# load the data from iemiscdata (containing Table 2-2c: Runoff curve numbers for other agricultural lands & notes)


pander(cn_other_agricultural)
pander(cn_other_agricultural_notes)

```

\bigskip
\bigskip

# Table 2-2d: Runoff curve numbers for arid and semiarid rangelands & notes

```{r, warning = FALSE, message = FALSE, tidy = TRUE}

data(cn_arid_semiarid)
data(cn_arid_semiarid_notes)
# load the data from iemiscdata (containing Table 2-2d: Runoff curve numbers for arid and semiarid rangelands & notes)


pander(cn_arid_semiarid)
pander(cn_arid_semiarid_notes)

```

\bigskip
\bigskip

# Table from Appendix A: Hydrologic Soil Groups (HSGs) & notes

```{r, warning = FALSE, message = FALSE, tidy = TRUE}

data(hsg)
data(hsg_definitions)
# load the data from iemiscdata (containing Table from Appendix A: Hydrologic Soil Groups (HSGs) & notes)



pander(hsg)
pander(hsg_definitions)

```

\bigskip
\bigskip

# US EPA National Primary Drinking Water Regulations Contaminants Table & notes

```{r, warning = FALSE, message = FALSE, tidy = TRUE}
data(USA_primary_water_contaminants)
data(USA_primary_water_contaminants_notes)
# load the data from iemiscdata (containing US EPA National Primary Drinking Water Regulations Contaminants Table & notes)



pander(USA_primary_water_contaminants)
pander(USA_primary_water_contaminants_notes)

```

\bigskip
\bigskip

# US EPA Secondary Drinking Water Standards Table & notes

```{r, warning = FALSE, message = FALSE, tidy = TRUE}
data(USA_secondary_water_contaminants)
data(USA_secondary_water_contaminants_notes)
# load the data from iemiscdata (containing US EPA Secondary Drinking Water Standards Table & notes)



pander(USA_secondary_water_contaminants)
pander(USA_secondary_water_contaminants_notes)

```

\bigskip
\bigskip

# Table 3-1: Roughness coefficients (Manning's n) for sheet flow

```{r, warning = FALSE, message = FALSE, tidy = TRUE}

data(nsheetflow)
data(nsheetflow_notes)
# load the data from iemiscdata (containing Table 3-1: Roughness coefficients (Manning's n) for sheet flow & notes)



pander(nsheetflow)
pander(nsheetflow_notes)

```

\bigskip
\bigskip

# Greenhouse Gases -- Percent Contribution to Total Greenhouse Effect (Wikipedia)

```{r, warning = FALSE, message = FALSE, tidy = TRUE}

data(greenhouse_gases_cloudy_wikipedia)
data(greenhouse_gases_cloudy_notes_wikipedia)
# load the data from iemiscdata [containingGreenhouse Gases -- Percent Contribution to Total Greenhouse Effect & notes (Wikipedia)]



pander(greenhouse_gases_cloudy_wikipedia)
pander(greenhouse_gases_cloudy_notes_wikipedia)

```

\bigskip
\bigskip
\bigskip
\bigskip

# Data Sources

United States Department of Agriculture Natural Resources Conservation Service Conservation Engineering Division, "Urban Hydrology for Small Watersheds Technical Release 55 (TR-55)", June 1986, pages 2-3, 2-5 - 2-8, 3-3, 4-1 - 4-2, A-1, https://web.archive.org/web/20230810204711/https://directives.sc.egov.usda.gov/OpenNonWebContent.aspx?content=22162.wba [Recovered with the Internet Archive: Wayback Machine]  

United States (US) Environmental Protection Agency (EPA): "National Primary Drinking Water Regulations", https://www.epa.gov/ground-water-and-drinking-water/national-primary-drinking-water-regulations.  

United States (US) Environmental Protection Agency (EPA): "Secondary Drinking Water Standards: Guidance for Nuisance Chemicals", https://www.epa.gov/sdwa/secondary-drinking-water-standards-guidance-nuisance-chemicals.  

Wikimedia Foundation, Inc. Wikipedia, 25 August 2023, "Greenhouse gas", https://en.wikipedia.org/wiki/Greenhouse_gas.  

\bigskip
\bigskip

# EcoC²S Links

EcoC²S Home -- https://www.ecoccs.com/  
About EcoC²S -- https://www.ecoccs.com/about-ecoc2s.html  
Services -- https://www.ecoccs.com/services.html  
1 Stop Shop -- https://www.ecoccs.com/other-biz.html  
Products -- https://www.questionuniverse.com/products.html  
Media -- https://www.ecoccs.com/media.html  
Resources -- https://www.ecoccs.com/resources.html  
R Trainings and Resources provided by EcoC²S (Irucka Embry, E.I.T.) -- https://www.ecoccs.com/rtraining.html  

\bigskip
\bigskip

# Copyright and License

All R code written by Irucka Embry is distributed under the GPL-3 (or later) license, see the [GNU General Public License {GPL} page](https://www.gnu.org/licenses/gpl-3.0.html).  

All written content originally created by Irucka Embry is copyrighted under the Creative Commons Attribution-ShareAlike 4.0 International license. All other written content retains the copyright of the original author(s).  

This work is licensed under a [Creative Commons Attribution-ShareAlike 4.0 International license](https://creativecommons.org/licenses/by-sa/4.0/).  
