---
title: "iemiscdata: PDF Version of Manning&#8217;s n Tables"
author: "Irucka Embry, E.I.T. (EcoC²S)"
date: "`r Sys.Date()`"
lang: en-us
urlcolor: blue
output:
  rmarkdown::pdf_document:
    highlight: kate
    toc: true
    latex_engine: xelatex
vignette: >
  %\VignetteIndexEntry{iemiscdata PDF Version of Manning's n Tables}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

\bigskip

# View PDF version of the tables

If you would like to view the PDF tables, then use the code below that matches your operating system:  

\bigskip
\bigskip

# under Unix-based operating systems

Source: [Show me the pdf already | R-bloggers By Will](https://www.r-bloggers.com/2013/02/show-me-the-pdf-already/)  

\medskip

```{r eval = FALSE}
pdf <- getOption("pdfviewer", default = "")

f <- system.file("pdf", "Mannings_n_Values.pdf", package = "iemiscdata")

system2(pdf, args = f)
```

\bigskip
\bigskip

# under MS Windows operating systems

Source: [Show me the pdf already | R-bloggers By Will](https://www.r-bloggers.com/2013/02/show-me-the-pdf-already/)  

\medskip

```{r eval = FALSE}
f <- system.file("pdf", "Mannings_n_Values.pdf", package = "iemiscdata")

shell.exec(normalizePath(f))
```

\bigskip
\bigskip

# under OS X operating systems

Source: [Opening PDF within R studio using file.show - Stack Overflow](https://stackoverflow.com/questions/33791493/opening-pdf-within-r-studio-using-file-show/33791818)  

\medskip

```{r eval = FALSE}

f <- system.file("pdf", "Mannings_n_Values.pdf", package = "iemiscdata")

system2("open", args = f, wait = FALSE)
```

\bigskip
\bigskip

# EcoC²S Links

EcoC²S Home -- https://www.ecoccs.com/  
About EcoC²S -- https://www.ecoccs.com/about_ecoc2s.html  
Services -- https://www.ecoccs.com/services.html  
1 Stop Shop -- https://www.ecoccs.com/other_biz.html  
Products -- https://www.questionuniverse.com/products.html  
Media -- https://www.ecoccs.com/media.html  
Resources -- https://www.ecoccs.com/resources.html  
R Trainings and Resources provided by EcoC²S (Irucka Embry, E.I.T.) -- https://www.ecoccs.com/rtraining.html  

\bigskip
\bigskip

# Copyright and License

All R code written by Irucka Embry is distributed under the GPL-3 (or later) license, see the [GNU General Public License {GPL} page](https://www.gnu.org/licenses/gpl-3.0.html).  

All written content originally created by Irucka Embry is copyrighted under the Creative Commons Attribution-ShareAlike 4.0 International License. All other written content retains the copyright of the original author(s).  

This work is licensed under a [Creative Commons Attribution-ShareAlike 4.0 International License](https://creativecommons.org/licenses/by-sa/4.0/).  
