---
title: "PDF Version of Manning's n Tables"
author: "Irucka Embry"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_document:
    highlight: kate
    theme: readable
vignette: >
  %\VignetteIndexEntry{Viewing Manning's n Tables as a PDF}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<br />
<br />

# View PDF version of the tables

If you would like to view the PDF tables, then use the code below that matches your operating system:

<br />

# under Unix-based operating systems

Source: [Show me the pdf already | R-bloggers By Will](http://www.r-bloggers.com/show-me-the-pdf-already/)
```{r eval = FALSE}
pdf <- getOption("pdfviewer", default = "")
f <- system.file("pdf", "Mannings_n_Values.pdf", package = "iemiscdata")
system2(pdf, args = f)
```

<br />
<br />

# under MS Windows operating systems

Source: [Show me the pdf already | R-bloggers By Will](http://www.r-bloggers.com/show-me-the-pdf-already/)
```{r eval = FALSE}
f <- system.file("pdf", "Mannings_n_Values.pdf", package = "iemiscdata")
shell.exec(normalizePath(f))
```

<br />
<br />

# under OS X operating systems

Source: [Opening PDF within R studio using file.show - Stack Overflow -- rensa](http://stackoverflow.com/questions/33791493/opening-pdf-within-r-studio-using-file-show/33791818)
```{r eval = FALSE}
f <- system.file("pdf", "Mannings_n_Values.pdf", package = "iemiscdata")
system2("open", args = f, wait = FALSE)
```
